%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {NLP Engineer} % Job title
    {Yale University - School of Medicine} % Organization
    {New Haven, USA (Remote)} % Location
    {May. 2022 - Currently} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I am in charge of Data Ops development, specifically for all matters related to biographical information of faculty members in the School of Medicine.}
        \item {I develop pipelines for the data engineering process, focusing on the information derived from medical records in order to analyze this data.}
        \item {As the leader of the NLP team, I am responsible for developing tools that aid the School of Medicine in matters of document assistance.}
        \item {I also spearhead research on computational inference for optimizing the MLOps process.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Data Scientist} % Job title
    {InterAmerican Development Bank} % Organization
    {Washington, USA (Remote)} % Location
    {Jul. 2020 - Currently} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I am in charge of developing AI for project evaluation and risk assessment in social development projects in LATAM, under the criteria of political science, macroeconomics, and the current state of each member country.}
        \item {I develop recommendation system models for designing public policy proposals aimed at promoting social development in member countries.}
        \item {I developed the deployment architecture on AWS for analytics products.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Tech Lead} % Job title
    {Mercado Libre} % Organization
    {Colombia} % Location
    {Jan. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I led a team of data scientists and data engineers in developing Pricing, Forecasting, complementary product information, and user fraud detection products.}
        \item {I developed a pricing model for Argentina, Brazil, and Mexico using Bayesian tools and time series analysis to determine the best price for purchasing a car in dynamic auctions, while maintaining the desired profit margin from its sale.}
        \item {I also developed an anomaly detection model to identify instances of potential user impersonation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Data Scientist} % Job title
    {Chiper} % Organization
    {Bogotá, Colombia} % Location
    {Jul. 2019 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I developed the first MLOps architecture on GCP for deploying machine learning products.}
        \item {I created demand prediction models for over 200 SKUs.}
        \item {I evaluated the most effective way to distribute products, minimizing delivery times and reaching the greatest number of customers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Secretaría de Educación de Bogotá} % Organization
    {Bogotá, Col} % Location
    {Aug. 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I developed the first sample models based on Bayesian methods to understand the disaggregated behavior of the population in terms of public policies.}
        \item {I created Item Response Theory models for designing development strategies for primary education in Mathematics and English.}
        \item {I developed the first AI model that wrote reports for each district institution, evaluating and drawing conclusions on the education performance by school and by student.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {ONU} % Organization
    {Santiago de Chile, Chile} % Location
    {May. 2013 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I developed criminal detection models using Data Science and mathematical tools.}
        \item {I created dynamic maps to determine the types of crimes that could occur by hour and area.}
        \item {I conducted psychometric research to assess the state of individuals who committed crimes in Santiago, Chile.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
